A Practical Optional Type System for Clojure

### 2012-10-24 dissertation/intro.tex
Fix incomplete references

There are many concepts associated with \emph{types} and \emph{type systems} in both the
literature and informal discourse.
A programmer who uses dynamically-typed languages may have a drastically different notion
of what a type is than, say, a programmer preferring languages with advanced static type systems.
There is some debate as to whether optional static type systems like Typed Clojure
can even be called a type system. We choose to
follow the terminology of Pfenning~\cite{Pfe08} and Reynolds~\cite{Rey01},
where such optional type systems are \emph{extrinsic} type systems, and more
traditional type systems are \emph{intrinsic} type systems.
This distinction has a long history, originating in work in the $\lambda$-calculus 
by Church~\cite{Chu40} and Curry~\cite{Cur34},
leading to intrinsic types and extrinsic types also being called Church types and
Curry types often in the literature.

>>>>

There are many concepts associated with \emph{types} and \emph{type systems} in both the
literature and informal discourse.
A programmer who uses dynamically-typed languages may have a drastically different notion
of what a type is than, say, a programmer preferring languages with advanced static type systems.
There is some debate as to whether optional static type systems like Typed Clojure
can even be called a type system. We choose to
follow the terminology of Pfenning~\cite{Pfe08} and Reynolds~\cite{Rey02},
where such optional type systems are \emph{extrinsic} type systems, and more
traditional type systems are \emph{intrinsic} type systems.
This distinction has a long history, originating in work in the $\lambda$-calculus 
by Church~\cite{Chu40} and Curry~\cite{Cur34},
leading to intrinsic types and extrinsic types also being called Church types and
Curry types often in the literature.
